How is experience transformed into memory?

### 2018-09-03 paper/main.tex
paxton noticed more stuff, thereby solidifying his position as real-world sherlock holmes

\subsubsection*{Estimating the consistency of flow through topic space across participants}
In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space for which we can predict that

>>>>

\subsubsection*{Estimating the consistency of flow through topic space across participants}
In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).  The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) ranged from -6 to 6 (arbitrary) units, in both the $x$ and $y$ dimensions.  We divided this space into a grid of vertices spaced 0.25~units apart.  For each square, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units of its center.
